Generating Performance Improvement Suggestions by using Cross-Organizational Process Mining

### 2015-11-21 5_results_discussions/results_discussions.tex
no message
Shortening

\section{Results and Discussions}
\label{sec:results-and-discussions}

@@

Approach in this study is an aggregation of various methods and they are significantly different from each other in their mathematical background. Therefore, instead of a global evaluation metric for the complete methodology, each stage is evaluated within its evaluation metrics which are as follows:
\begin{description}
	\item[Process Model Mining] Performance of process mining stage is measured by \textit{fitness} and \textit{appropriateness} which are defined in \cite{rozinat2008conformance}.
	\item[Performance Indicator Analysis] In replay phase, \textit{alignment costs} \cite{van2012replaying} are compared with process model mining metrics. In clustering phase, \textit{within-SSE} analysis is undertaken to decide on the number of clusters.
	\item[Mismatch Pattern Analysis] In this stage, number of mismatch patterns found are compared with the \textit{graph-edit similarity} \cite{dijkman2011similarity} of process models.
	\item[Recommendation Generation] In recommendation generation, different threshold values are tried to check how many mismatch patterns are generated for organizations and how they could be used for focused analysis.
\end{description}

>>>>

\section{Experimental Analysis Results and Discussions}
\label{sec:results-and-discussions}

@@

Approach in this study is an aggregation of various methods and they are significantly different from each other in their mathematical background. Therefore, instead of a global evaluation metric for the complete methodology, each stage is evaluated within its evaluation metrics. In \textit{process model mining}, performance of process mining stage is measured by \textit{fitness} and \textit{appropriateness} which are defined in \cite{rozinat2008conformance}. In \textit{performance indicator analysis}, \textit{alignment costs} \cite{van2012replaying} are compared with process model mining metrics for replay phase. In clustering phase, \textit{within-SSE} analysis is undertaken to decide on the number of clusters. For \textit{mismatch pattern analysis}, number of mismatch patterns found are compared with the \textit{graph-edit similarity} \cite{dijkman2011similarity} of process models. In \textit{recommendation generation}, different threshold values are tried to check how many mismatch patterns are generated for organizations and how they could be used for focused analysis.
